### 2015-06-23 paper/main.tex
added paper

\title{Chum Populations}

\documentclass[12pt,  one column]{article}

\begin{document}

\section*{Abstract}

\section*{Introduction}

\section*{Methods}

\section*{Results}

Identification of paralogs
congruence of paralog across families (supplemental table)
Consensus linkage map
Table (Figure?)
placement of centromeres
table (supplemental)
paralogs
note the distribution of paralogs matches the  pattern found in other salmonids
syntenic relationships - per LG
Table (supplemental?)
Population genetics
Summarize population relationships
Figure of individual-based 4 PCAs
measure information loss from dominance coding
discuss population vs individual based results
paralogs have similar neutral patterns of population structure.
can we demonstrate contained within paralogs by bootstrapping 
Genome scans (Outliers) - LG regions highlighted.
Effective population size

Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.

\section*{Discussion}

%To insert image:
%\begin{center}
%\includegraphics[scale=.8]{ProblemSet3Graph2.png}
%\end{center}
%Note that the file must be in the same folder. 
boo

\end{document}

### 2015-06-24 paper/main.tex
added paper, added Ne

@@
 \documentclass[12pt,  one column]{article}
+\usepackage{graphicx}
 
@@
 
+Dominance coding \cite{}
+
+ - measure information loss
+
+\subsection*{Effective population size}
+
+\subsection*{Ascertainment Bias}
+
 \section*{Results}
 
+\subsection*{Linkage map}
 Identification of paralogs
+
 congruence of paralog across families (supplemental table)
+
 Consensus linkage map
+
 Table (Figure?)
 placement of centromeres
+
 table (supplemental)
@@
 Population genetics
+
 Summarize population relationships
 Figure of individual-based 4 PCAs
+
+\includegraphics[scale=.3]{figures/PCA_codom.png}
+\includegraphics[scale=.3]{figures/PCA_dom.png}
+
+\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
+\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
+
 measure information loss from dominance coding
@@
 Genome scans (Outliers) - LG regions highlighted.
-Effective population size
 
+\subsection*{Effective population size}
+
+\subsection*{Ascertainment Bias}
 Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
@@
 
-%To insert image:
+\section*{Supplemental}
+
+%\includegraphics[scale=.4]{figures/supplemental/ascertainment.png}
+
+\includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
+
+%\includegraphics[scale=.4]{figures/supplemental/TW_stats.png}
+
+%\begin{figure}
 %\begin{center}
-%\includegraphics[scale=.8]{ProblemSet3Graph2.png}
+%\includegraphics[scale=.3]{figures/supplemental/analysis_flowchart.png}
 %\end{center}
-%Note that the file must be in the same folder. 
-boo
+%\end{figure}
 

### 2015-06-25 paper/main.tex
synteny, Ne, and paper updates

@@
 \usepackage{graphicx}
+\usepackage{float}
 
@@
 
+Does this turn into two papers?
+
+ - linkage map and individual-based analyses - including duplicated loci
+
+ - inference of adaptation - life history variation  - Fst across the genome.
+
 \section*{Abstract}
+To do
 
 \section*{Introduction}
+To do
+
+Expected population structure
+
+ESA listing - summer chum ESU
+
+Salmonid WGD
 
@@
 
-Dominance coding \cite{}
+\subsection*{Linkage map}
 
- - measure information loss
+Sequence analysis and genotyping
 
-\subsection*{Effective population size}
+Identification of paralogs follows Waples (2015)
 
-\subsection*{Ascertainment Bias}
+Map construction follows Waples (2015)
+
+Synteny - relation to genetic resources
+\begin{itemize}
+	\item Chinook salmon
+    \item Atlantic salmon
+\end{itemize}
+
+\subsection*{Population Genetics}
+Sequence analysis and genotyping
+
+Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
+Individual-based analyses
+\begin{itemize}
+	\item PCAs - How do compare? - maybe measure info loss?
+    \item Heterozygosity
+	\item Fst across the genome
+\end{itemize}
+
+Population-based analyses
+\begin{itemize}
+	\item MAF, Heterozygosity
+	\item Fst across the genome
+    \item Effective population size - Waples and Do
+    \item Bayescan outlier tests
+\end{itemize}
 
@@
 Table (supplemental?)
-Population genetics
+
+\subsection*{Population Genetics}
 
@@
 \includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
+\subsection*{Population Genetics}
 
@@
 \section*{Discussion}
+To do
 
@@
 
-%\includegraphics[scale=.4]{figures/supplemental/ascertainment.png}
+\begin{figure}[H]
+\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
+\caption{Minor allele frequency distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green). The increase in MAF shows the effect of ascertainment bias.}
+\end{figure}
 
+\begin{figure}[H]
 \includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
+\caption{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.  Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
+\end{figure}
 
-%\includegraphics[scale=.4]{figures/supplemental/TW_stats.png}
+\begin{figure}[H]
+\includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
+\caption{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.  Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[scale=.4]{figures/supplemental/TW_stats.png}
+\caption{Number of significant PC axes as determined by the Tracey-Widom test.}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[scale=.4]{figures/supplemental/synteny_chinook.png}
+\caption{Oxford grid - Chum and Chinook linkag groups.}
+\end{figure}
 

### 2015-07-06 paper/main.tex
genome scan notebook and work

@@
 
-Does this turn into two papers?
-
- - linkage map and individual-based analyses - including duplicated loci
-
- - inference of adaptation - life history variation  - Fst across the genome.
-
 \section*{Abstract}
@@
 \section*{Introduction}
-To do
 
-Expected population structure
+\begin{itemize}
 
-ESA listing - summer chum ESU
+\item PS chum pop gen
+\begin{itemize}
+\item Population structure
+\item life history variation
+\item ESA listing - summer chum ESU
+\item Effective population size
+\end{itemize}
 
-Salmonid WGD
+\item Genome scan
+\begin{itemize}
+\item paired population design
+\item map-assisted
+\item draw on synteny / orthology
+\end{itemize}
+
+\item Genotyping duplicates
+\begin{itemize}
+\item Legacy of the salmonid WGD
+\item uncharacterized regions of the genome
+\item first approach in salmon using next-gen seq data.  Method applicable to other species with WGD?
+
+\end{itemize}
+
+\item Map
+\begin{itemize}
+\item consensus map w/centromeres
+\item synteny
+\item annotation
+\end{itemize}
+
+\end{itemize}
 
 \section*{Methods}
+
+\subsection*{Population Genetics}
+Sequence analysis and genotyping
+
+Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
+Individual-based analyses
+\begin{itemize}
+    \item PCAs - How do these two methods compare? - maybe measure info loss?
+    \item Formal tests for population structure - tracey-widom stats
+
+\end{itemize}
+
+Population-based analyses
+\begin{itemize}
+	\item MAF, Heterozygosity
+    \item phylogenetic tree
+	\item Fst across the genome
+    \item Effective population size -
+
+    	Effective population size was estimated for each population using the LD method implemented in the LDNe software package (Waples and Do).
+The LD methods estimates average  correlation of alleles at pairs of loci (r2).
+The mean pairwise r2 value across unlinked loci provides an estimate of contemporary effective population size (WAPLES).
+The linkage map was used to ensure that only pairs of loci not co-located on a chromosome were used to calculate mean r2.
+    \item Bayescan outlier tests
+\end{itemize}
 
@@
 
-Map construction follows Waples (2015)
+Map construction follows McKinney (2015), based off Waples (2015)
 
@@
 
+\section*{Results}
+
 \subsection*{Population Genetics}
-Sequence analysis and genotyping
 
-Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
-Individual-based analyses
-\begin{itemize}
-	\item PCAs - How do compare? - maybe measure info loss?
-    \item Heterozygosity
-	\item Fst across the genome
-\end{itemize}
+Summarize population relationships
+Figure of individual-based 4 PCAs
 
-Population-based analyses
-\begin{itemize}
-	\item MAF, Heterozygosity
-	\item Fst across the genome
-    \item Effective population size - Waples and Do
-    \item Bayescan outlier tests
-\end{itemize}
+\includegraphics[scale=.3]{figures/PCA_codom.png}
+\includegraphics[scale=.3]{figures/PCA_dom.png}
 
-\section*{Results}
+\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
+\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
+paralogs have similar neutral patterns of population structure.
+measure information loss from dominance coding
+
+discuss population vs individual based results
+
+can we demonstrate contained within paralogs by bootstrapping 
+Genome scans - LG regions highlighted.
+
+\subsection*{Effective population size}
+
+\subsection*{Ascertainment Bias}
+Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
 
@@
 
-congruence of paralog across families (supplemental table)
+congruence of identified homeologs across families (supplemental table)
 
@@
 
-\subsection*{Population Genetics}
-
-Summarize population relationships
-Figure of individual-based 4 PCAs
-
-\includegraphics[scale=.3]{figures/PCA_codom.png}
-\includegraphics[scale=.3]{figures/PCA_dom.png}
-
-\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
-\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
-\subsection*{Population Genetics}
-
-measure information loss from dominance coding
-discuss population vs individual based results
-paralogs have similar neutral patterns of population structure.
-can we demonstrate contained within paralogs by bootstrapping 
-Genome scans (Outliers) - LG regions highlighted.
-
-\subsection*{Effective population size}
-
-\subsection*{Ascertainment Bias}
-Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
-
 \section*{Discussion}
@@
 
+Coalescent!
+
+Does this turn into two papers?
+
+ - linkage map and individual-based analyses - including duplicated loci
+
+ - inference of adaptation -associated  life history variation  - Fst across the genome.
+
+\pagebreak
 \section*{Supplemental}
@@
 \includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
-\caption{Minor allele frequency distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green). The increase in MAF shows the effect of ascertainment bias.}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
-\caption{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.  Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
+\caption{Minor allele frequency (MAF) distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green).
+The rightward shift in the MAF distributino shows the effect of ascertainment bias within the mapped loci.}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[scale=.4]{figures/supplemental/synteny_chinook.png}
-\caption{Oxford grid - Chum and Chinook linkag groups.}
+\includegraphics[scale=.25]{figures/supplemental/synteny_chinook.png}
+\caption{Oxford grid - Chum and Chinook linkage groups.  Loci are positioned according to the order within each genome.}
 \end{figure}

### 2015-07-06 scripts/Fst_genome_scan_plots.r

@@ -1,0 +1,44 @@
+library(ggplot2)
+library(RColorBrewer)
+
+FDR =.05
+
+#load base data
+map_fst = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/pop_analysis/map_fst.txt', header = TRUE,sep = "\t")
+
+
+
+map_fst$outlier = map_fst$qval < FDR
+map_fst$LG = map_fst$paper1_LG
+
+
+ggplot(map_fst, aes(x=cM, y=BS_Fst)) + 
+  facet_grid(LG ~ .) +
+  geom_point(aes(color=outlier), alpha = .7, size = 3) +
+  scale_color_manual(values=c("darkgrey","red")) +
+  stat_smooth(fill="blue", colour="darkblue", size=2, alpha = 0.1, method = 'loess', span=0.3, n = 10) +
+  theme_bw() + theme(strip.text = element_blank()) + 
+  theme(strip.text = element_text(size=20))
+ggsave('/home/ipseg/Desktop/waples/chum_populations/paper/figures/supplemental/Fst_across_the_genome.png', height=48, width=12)
+
+ggplot(map_fst, aes(x=cM, y=WC_Fst)) + 
+  facet_grid(LG ~ .) +
+  geom_point(aes(color=outlier), alpha = .7, size = 3) +
+  scale_color_manual(values=c("darkgrey","red")) +
+  stat_smooth(fill="blue", colour="darkblue", size=2, alpha = 0.1, method = 'loess', span=0.5, n = 20) +
+  theme_bw() + theme(strip.text = element_blank()) + 
+  theme(strip.text = element_text(size=20))
+ggsave('/home/ipseg/Desktop/waples/chum_populations/paper/figures/supplemental/Fst_across_the_genome.png', height=48, width=12)
+
+
+names
+
+xx = map_fst[map_fst$LG ==10,]$cM
+yy = map_fst[map_fst$LG ==10,]$BS_Fst
+#yy[yy > 10000] = 5
+scatter.smooth(xx, yy, span = .1, degree = 2, evaluation =100)
+
+xx = map_fst[map_fst$LG ==8,]$cM
+yy = map_fst[map_fst$LG ==8,]$BS_Fst
+#yy[yy > 10000] = 5
+scatter.smooth(xx, yy, span = .5, degree = 2, evaluation =100)

### 2015-07-15 paper/main.tex
added bibtex, remade oxford grid

@@
 \usepackage{float}
+\usepackage{enumitem}
+\usepackage{natbib}
 
 \begin{document}
+% \bibliographystyle{}
 
 \section*{Abstract}
-To do
+None yet
 
-\section*{Introduction}
-
+\section*{Outline}
 \begin{itemize}
 
-\item PS chum pop gen
+\item Puget Sound chum salmon populations
 \begin{itemize}
 \item Population structure
-\item life history variation
+\item chum salmon anadromous life history - 
 \item ESA listing - summer chum ESU
 \item Effective population size
-\end{itemize}
-
-\item Genome scan
-\begin{itemize}
-\item paired population design
-\item map-assisted
-\item draw on synteny / orthology
 \end{itemize}
@@
 \item uncharacterized regions of the genome 
-\item first approach in salmon using next-gen seq data.  Method applicable to other species with WGD?
+\item first approach in salmon using next-gen seq data.
+\end{itemize}
 
+\item Genome scan
+\begin{itemize}
+\item map-assisted
+\item paired population design
+\item draw on synteny / orthology to interpret results
 \end{itemize}
@@
 \begin{itemize}
-\item consensus map w/centromeres
+\item consensus map
 \item synteny
+\item annotation
+\end{itemize}
+
+\end{itemize}
+
+\pagebreak
+
+\section*{Introduction}
+\begin{itemize}
+
+\item Puget Sound chum salmon populations
+\begin{itemize}
+\item Population structure
+Wild distribution
+
+Two Evolutionary significant units (ESU) - Hood canal summer vs the rest.
+'Genetically and ecologically distinct' threatened under the ESA.
+Notice which populations where supplemented by hatchery programs?
+Chum salmon stray at similar rates to other pacific salmon \cite{Small2014} (also could cite johnson et al 1997).
+
+\item chum salmon anadromous life history - 
+eggs deposited nov-dec
+embryos devlop and hatch after ~4 months coupled with a migration to sea.
+'survival and growth in juvenile chum salmon depend less on freshwater conditions than on favorable estuarine and marine conditions.'
+return to spawn at 3-5 years of age, spawn within 100km of the ocean
+
+\item life history variation
+\item ESA listing - summer chum ESU
+\item Effective population size
+\end{itemize}
+
+\item Genotyping duplicates
+\begin{itemize}
+\item Legacy of the salmonid WGD
+\item uncharacterized regions of the genome - retained through unknown mechanisms.
+Possible benefits are unknown but could include reduced inbreeding depression in small isolated populations typical of salmonids.
+\item This is the first time that high-throughput sequencing data has been applied to score duplicated loci within salmonids.
+\end{itemize}
+
+\item Genome scan
+\begin{itemize}
+\item map-assisted
+\item paired population design
+\item draw on synteny / orthology to interpret results
+\end{itemize}
+
+\item Map
+\begin{itemize}
+\item A consensus linkage map was constructed from three gynogenetic haploid families (sizes 175, 4x, 3x).
+This linkage map is novel but builds on the map presented in \citet{Waples2015} with the addition of two additional families.
+Within each linkage group, we estimate the location of the centromere (cite morten?).
+
+Paralogous loci were identified by through their segregation patterns as in \citet{Waples2015}.  At each locus, the observed allelic segregation pattern were fit to multiple models specified by
+
+\item The othologous loci and 
 \item annotation
@@
 \subsection*{Population Genetics}
-Sequence analysis and genotyping
+\subsubsection*{Sequence analysis and genotyping}
+\begin{itemize}[nosep]
+\item Varaint SNPs were identified and genotyped with a reference-based approach with the Stacks software pipeline \cite{Catchen2013}.  Reference constructed from \citet{Waples2015}
+\item alignment with BWA-mem, remove low-quality alignments
+\item identify variants and assign genotypes with pstacks
+\item filter genotypes and individuals to produce final data set. 
+\item Does allelic bias filtration have a place here?
+\end{itemize}
 
-Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
+\subsubsection*{Individual-based analyses} 
+\begin{itemize}[nosep]
+	\item Genotyping duplicate loci using the dominance coding suggested by \cite{Patterson2006}. 
 Individual-based analyses
-\begin{itemize}
 	\item PCAs - How do these two methods compare? - maybe measure info loss?
-    \item Formal tests for population structure - tracey-widom stats
+    Use a Procrustes analysis to find an optimal transformation.
+This allows the superimposition of one result onto another set of axes, through rotation and stretching.
+produced a procrustes similarity \cite{Peres2001}.
+Other option is a CCA (canonical correlation analysis)
+    \item Formal tests for population structure - tracey-widom stats.  Breakdown of population structure and lower PC axes
 
@@
 
-Population-based analyses
-\begin{itemize}
+\subsubsection*{Population-based analyses}
+
+\begin{itemize}[nosep]
 	\item MAF, Heterozygosity
     \item phylogenetic tree
-	\item Fst across the genome
+    \item Genome scan - gloabal or paired populations - 	
+    \item Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)
     \item Effective population size -
 
-    	Effective population size was estimated for each population using the LD method implemented in the LDNe software package (Waples and Do).
+    	Effective population size was estimated for each population using the LD method implemented in the LDNe software package \cite{Waples2010}.
 The LD methods estimates average correlation of alleles at pairs of loci (r2).
-The mean pairwise r2 value across unlinked loci provides an estimate of contemporary effective population size (WAPLES).
+The mean pairwise r2 value across unlinked loci provides an estimate of contemporary effective population size.
 The linkage map was used to ensure that only pairs of loci not co-located on a chromosome were used to calculate mean r2.
-    \item Bayescan outlier tests
+
+Run this with and without the linkage map correction \cite{Larson2014}?
+
 \end{itemize}
@@
 
-Identification of paralogs follows Waples (2015)
+%Identification of paralogs follows \cite{Waples2015}
 
-Map construction follows McKinney (2015), based off Waples (2015)
+Map construction follows McKinney (2015), Waples (2015)
 
 Synteny - relation to genetic resources
-\begin{itemize}
+\begin{itemize}[nosep]
 	\item Chinook salmon
@@
 
+\pagebreak
 \section*{Results}
 
+Genotyping rate
 \subsection*{Population Genetics}
+population structure
 
-Summarize population relationships
-Figure of individual-based 4 PCAs
+Summarize population relationships, consistent with \citet{Small2014}?
+
+Four individual-based PCA figures
 
@@
 \includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
-paralogs have similar neutral patterns of population structure.
-measure information loss from dominance coding
+Paralogs have similar neutral patterns of population structure (Procrustes similarity xxx)
+
+Is the a possible quantitative measure of information loss due to dominance coding?  These doesn't quite make sense, as the the dominant haplotypes contain *more* information.
 
@@
 
+Perhaps run the Ne with and without the linkage map correction?
+
 \subsection*{Ascertainment Bias}
+The linkage map was constructed from three female parents from Hoodsport hatchery, WA.
+
 Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
 
+\begin{figure}[H]
+\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
+\caption{Minor allele frequency (MAF) density histograms for all loci (blue) and the subset of loci placed on the linkage map (green).
+The rightward shift in the MAF distribution shows the effect of ascertainment bias.} \textbf{TODO: align histogram bins, check the .5 boundary}
+\end{figure}
+
 \subsection*{Linkage map}
-Identification of paralogs
+Here we present a consensus map placing XXX loci onto 37 linkage groups.
+These 37 linkage groups likely have a 1:1 correspondence with the 37 chromosomes in chum salmon.
+\textbf{Do we want a map figure, or just a table?}
 
-congruence of identified homeologs across families (supplemental table)
+A total of xxx paralogs were identified and placed onto the linkage map.
+The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with Identification of paralogs, congruence of identified homeologs across families (supplemental table)
 
-Consensus linkage map
-
-Table (Figure?)
 placement of centromeres
 
-table (supplemental)
 paralogs
-note the distribution of paralogs matches the  pattern found in other salmonids
-syntenic relationships - per LG
+
+Notice the distribution of paralogs matches the  pattern found in other salmonids.
+syntenic/orthologous relationships - per LG
 Table (supplemental?)
@@
 
-Coalescent!
+Compared to \citet{Small2014} the effective sizes (N$_{e}$) are larger, this could be due to the downward bias removed by utilizing the linkage map.
 
@@
 \section*{Supplemental}
-
-\begin{figure}[H]
-\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
-\caption{Minor allele frequency (MAF) distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green).
-The rightward shift in the MAF distributino shows the effect of ascertainment bias within the mapped loci.}
-\end{figure}
 
@@
 
+\section*{Reference}
+
+\bibliographystyle{apalike}
+\bibliography{./bibtex/7_13_15}
+
+\section*{Acknowledgements}
+Rachel Hovel - advice woth multivariate stats.
+
 \end{document}

### 2015-07-29 paper/main.tex
update paper

@@
 
-\section*{Abstract}
-None yet
-
 \section*{Outline}
@@
 
+\item Genotyping duplicates
+\begin{itemize}
+\item Legacy of the salmonid WGD
+\item uncharacterized regions of the genome 
+\item first approach in salmon using next-gen seq data.
+\end{itemize}
+
+\begin{itemize}
+\item Genome scan
 \item Puget Sound chum salmon populations
@@
 
-\item Genotyping duplicates
-\begin{itemize}
-\item Legacy of the salmonid WGD
-\item uncharacterized regions of the genome 
-\item first approach in salmon using next-gen seq data.
-\end{itemize}
-
-\item Genome scan
-\begin{itemize}
-\item map-assisted
-\item paired population design
+\item map-assisted, paired population design
 \item draw on synteny / orthology to interpret results
@@
 
-\item Map
+\item Linkage Map
 \begin{itemize}
@@
 \pagebreak
+\section*{Abstract}
+The common ancestor of salmonids underwent a whole genome duplication (WGD) approximately 100 million years ago.
+Understanding the genetic legacy of this event is critical to the conservation and management of these economically and socially important fish species.
+In contrast to most animals with strictly disomic inheritance, regions of the salmon genome undergo tetrasomic inheritance.
+Loci in these regions are often excluded from genetic analyses owing to increased complexity during both genotype assignment and subsequent analyses.
+Here I develop methods to better characterize the tetrasomically-inherited regions of salmonid genomes.
 
 \section*{Introduction}
-\begin{itemize}
 
-\item Puget Sound chum salmon populations
-\begin{itemize}
-\item Population structure
-Wild distribution
+\subsection*{Genotyping duplicates}
+Legacy of the salmonid WGD - Uncharacterized regions of the genome - retained through unknown mechanisms.
+Recent studies have shown the benefits of polyploidy in other species \citep{Selmecki2015}.
+Possible benefits are unknown but could include reduced inbreeding depression in small isolated populations typical of salmonids.
 
-Two Evolutionary significant units (ESU) - Hood canal summer vs the rest.
+This is the first time that high-throughput sequencing data has been applied to score duplicated loci within salmonids.
+
+map-assisted genome scan with a paired population design
+
+\subsection*{Puget Sound chum salmon populations}
+Population structure
+
+Salmonids in the Pacific Northwest have a rich variety of life histories, with variation in run-timing, straying rates, age at maturity, freshwater residence, and many other dimensions \citep{Quinn2005}.
+This species and population-level diversity adds resilience to ecosystems and to species of conservation and economic concern \citep{Schindler2010}, especially in the face of climate change (reviewed in \citet{Schindler2015}).
+
+Chum salmon (Oncorhynchus keta) have the widest distribution of any Pacific salmonid, from Korea, around the Pacific Rim, to Oregon \citep{Salo1991}.
+Chum salmon are abundant and are utilized by tribal and non-tribal fishers and comprise the dominant commercial fishery in Washington State.
+Recently some chum salmon populations have undergone drastic declines.
+National Oceanic and Atmospheric Administration (NOAA) Fisheries recognizes four evolutionarily significant units (ESUs) of chum salmon in the Pacific Northwest.
+Of the four, two are listed as ‘threatened’ under the Endangered Species Act: the Hood Canal summer-run ESU and the Columbia River ESU.
+The Hood Canal summer-run ESU is composed of 16 historic populations, 7 of which are extinct \citep{Good2005} and is the earliest-returning chum salmon stock in the Americas.
+
+Two evolutionary significant units (ESU) - Hood canal summer-run vs the rest.
 'Genetically and ecologically distinct' threatened under the ESA.
 Notice which populations where supplemented by hatchery programs?
-Chum salmon stray at similar rates to other pacific salmon \cite{Small2014} (also could cite johnson et al 1997).
+Chum salmon stray at similar rates to other pacific salmon \cite{Small2014} (could also cite Johnson et. al. 1997).
 
-\item chum salmon anadromous life history - 
 eggs deposited nov-dec
@@
 
-\item life history variation
-\item ESA listing - summer chum ESU
-\item Effective population size
-\end{itemize}
+Effective population size
 
-\item Genotyping duplicates
-\begin{itemize}
-\item Legacy of the salmonid WGD
-\item uncharacterized regions of the genome - retained through unknown mechanisms.
-Possible benefits are unknown but could include reduced inbreeding depression in small isolated populations typical of salmonids.
-\item This is the first time that high-throughput sequencing data has been applied to score duplicated loci within salmonids.
-\end{itemize}
+\subsection*{Interpretation}
+The linkage map will be used to interpret the population genomic data.
+They provide information on the genomic adjacency of loci and facilitate the  assessment of statistical independence between alleles.
+This can address the persistent problem of pseudoreplication, such as during the estimation of effective population size (e.g., \citet{Larson2014} or for marker development for mixed stock analysis.
+Kernel smoothing and bootstrapping (e.g., \citet{Hohenlohe2010} will be used to identify genomic regions with elevated level of divergence.
 
-\item Genome scan
-\begin{itemize}
-\item map-assisted
-\item paired population design
-\item draw on synteny / orthology to interpret results
-\end{itemize}
-
-\item Map
-\begin{itemize}
-\item A consensus linkage map was constructed from three gynogenetic haploid families (sizes 175, 4x, 3x).
-This linkage map is novel but builds on the map presented in \citet{Waples2015} with the addition of two additional families.
-Within each linkage group, we estimate the location of the centromere (cite morten?).
-
-Paralogous loci were identified by through their segregation patterns as in \citet{Waples2015}.  At each locus, the observed allelic segregation pattern were fit to multiple models specified by
-
-\item The othologous loci and 
-\item annotation
-\end{itemize}
-
-\end{itemize}
+draw on synteny / orthology
 
@@
 
-\subsection*{Population Genetics}
-\subsubsection*{Sequence analysis and genotyping}
-\begin{itemize}[nosep]
-\item Varaint SNPs were identified and genotyped with a reference-based approach with the Stacks software pipeline \cite{Catchen2013}.  Reference constructed from \citet{Waples2015}
-\item alignment with BWA-mem, remove low-quality alignments
-\item identify variants and assign genotypes with pstacks
-\item filter genotypes and individuals to produce final data set. 
-\item Does allelic bias filtration have a place here?
-\end{itemize}
+\subsection*{Sequence analysis}
+SNPs were identified and genotyped with a reference-based approach with the Stacks software pipeline \cite{Catchen2013}.
+Reference constructed from \citet{Waples2015}.
+Reads from each individual were aligned to the reference with BWA-mem  \citep{Li2013}  Alignments with indels or with a mapping quality < 30 were removed.
+Stacks components pstacks, cstacks, sstacks and populations were used to identify, genotype SNPs, and assign sequence haplotypes for each population collection.
 
-\subsubsection*{Individual-based analyses} 
-\begin{itemize}[nosep]
-	\item Genotyping duplicate loci using the dominance coding suggested by \cite{Patterson2006}. 
-Individual-based analyses
-	\item PCAs - How do these two methods compare? - maybe measure info loss?
-    Use a Procrustes analysis to find an optimal transformation.
-This allows the superimposition of one result onto another set of axes, through rotation and stretching.
-produced a procrustes similarity \cite{Peres2001}.
-Other option is a CCA (canonical correlation analysis)
-    \item Formal tests for population structure - tracey-widom stats.  Breakdown of population structure and lower PC axes
+Filter genotypes and individuals to produce final data set (does allelic bias filtration have a place here?)
 
-\end{itemize}
+Paralogous loci were identified by through their segregation patterns as in \citet{Waples2015}.
+At each locus, the observed allelic segregation pattern were fit to models specified by parental genotypes.
 
-\subsubsection*{Population-based analyses}
+\subsection*{Population-based analyses}
 
-\begin{itemize}[nosep]
-	\item MAF, Heterozygosity
-    \item phylogenetic tree
-    \item Genome scan - gloabal or paired populations - 	
-    \item Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)
-    \item Effective population size -
+MAF, Heterozygosity
+
+phylogenetic tree
+
+Genome scan - gloabal or paired populations -
+
+Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)
 
@@
 
-Run this with and without the linkage map correction \cite{Larson2014}?
+\subsection*{Individual-based analyses} 
+Genotyping duplicate loci using the dominance coding suggested by \cite{Patterson2006}.
 
-\end{itemize}
+PCAs - How do these two methods compare? - maybe measure info loss?
+
+Use a Procrustes analysis to find an optimal transformation.
+This allows the superimposition of one result onto another set of axes, through rotation and stretching this produces a procrustes similarity measure \cite{Peres2001}.
+Other option is a CCA (canonical correlation analysis).
+
+Formal tests for population structure - Tracey-Widom stats \citep{Tracy1994}.
 
@@
 
-Sequence analysis and genotyping
+We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 4x, 3x) with the programs LEPmap \citep{Rastas2013} and MSTmap \citep{Wu2008}.
+This linkage map is novel and builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
+The Kosambi mapping function \citep{Kosambi1943} will be used to relate recombination fraction to genetic distance  due to the presence of strong recombination interference in salmonid chromosome arms \citep{Thorgaard1983}.
+The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).
 
-%Identification of paralogs follows \cite{Waples2015}
+\subsection*{Synteny - relation to genetic resources}
 
-Map construction follows McKinney (2015), Waples (2015)
+Contigs assembled from paired-end sequence data \citet{Waples2015} will be aligned to genomic resources including the Atlantic salmon genome (Willie Davidson, personal communication), chum transcriptome \citep{Seeb2011}, as well as linkage maps of Chinook salmon (McKinney et al.
+in prep).
+By design, RADseq generates sequence data exclusively near restriction enzyme cut sites; alignments of RAD contigs to genomic resources relate RAD data to much larger genomic sections.
+These resources often have functional annotations, whole gene sequences, and reading frame information that is unavailable to RADseq projects, expanding my ability to interpret genetic differentiation in a biological context.
 
-Synteny - relation to genetic resources
-\begin{itemize}[nosep]
-	\item Chinook salmon
-    \item Atlantic salmon
-\end{itemize}
+Othologous loci in Chinook salmon
 
-\pagebreak
+annotation drawn from \citep{Waples2015}
+
 \section*{Results}
@@
 Genotyping rate
-\subsection*{Population Genetics}
+\subsection*{Population-based}
 population structure
@@
 Summarize population relationships, consistent with \citet{Small2014}?
+
+Breakdown of population structure and lower PC axes.
 
@@
 Here we present a consensus map placing XXX loci onto 37 linkage groups.
-These 37 linkage groups likely have a 1:1 correspondence with the 37 chromosomes in chum salmon.
-\textbf{Do we want a map figure, or just a table?}
+These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in chum salmon \citep{Phillips2001}.
+\textbf{Do we want a map figure, or just a table?}.
+
+Overlap with population data.
 
 A total of xxx paralogs were identified and placed onto the linkage map.
-The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with Identification of paralogs, congruence of identified homeologs across families (supplemental table)
+The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \textbf{few good citations here - Marine, Kodama, Waples, McKinney}.
+Consistency across families (see supplemental table xx)
+
+The consensus linkage map produced in chapter two will likely be similar to the single-family map produced in chapter one.
+The map produced in chapter one contained thousands of loci placed on 37 linkage groups, with eight pairs of homeologous chromosome arms.
+These pairs have elevated levels of sequence identity, likely due to ongoing tetrasomic inheritance.
+We expect to find a similar pattern in the other two families, this would provide validation of the methods developed in chapter one.
+Potentially more interesting, but less likely, are drastic differences such as chromosomal inversions or chromosome number polymorphisms.
+This type of chromosomal variation is documented within some salmon species \citep{Phillips2001}, but is not likely to be seen between these closely related families from Hoodsport Washington.
 
@@
 Notice the distribution of paralogs matches the  pattern found in other salmonids.
-syntenic/orthologous relationships - per LG
+syntenic/orthologous relationships, see supplemental figure xx.
+
 Table (supplemental?)
@@
 
+\section*{Meta}
 Does this turn into two papers?
@@
 \pagebreak
-\section*{Supplemental}
+\section*{Supplemental Figures}
 
@@
 \includegraphics[scale=.25]{figures/supplemental/synteny_chinook.png}
-\caption{Oxford grid - Chum and Chinook linkage groups.  Loci are positioned according to the order within each genome.}
+\caption{Oxford grid - Chum and Chinook linkage groups. Loci are colored by their LG assignment in chum salmon and positioned according to the order within each genome.}
 \end{figure}
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[scale=.3]{figures/supplemental/analysis_flowchart.png}
-%\end{center}
-%\end{figure}
-
-\section*{Reference}
+% \section*{References}
 
@@
 \section*{Acknowledgements}
-Rachel Hovel - advice woth multivariate stats.
+Carita Pascal - lab work and library prep.
 
+Seeb lab
+
+WDFW - chum salmon expertise.
+
+Rachel Hovel - multivariate stat advice.
 \end{document}

### 2015-08-07 paper/main.tex
figure for poster

@@
 These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in chum salmon \citep{Phillips2001}.
-\textbf{Do we want a map figure, or just a table?}.
+\textbf{Do we want a map figure, perhaps just a slice of a single LG, or a table?}.
 
-Overlap with population data.
+Of the xxx loci scored in wild collectionsm, xxx were placed on the linkage map, and covering all LGs.
 
 A total of xxx paralogs were identified and placed onto the linkage map.
-The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \textbf{few good citations here - Marine, Kodama, Waples, McKinney}.
+The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015} (also McKinney submitted).
 Consistency across families (see supplemental table xx)

### 2015-08-14 paper/main.tex
paper figures, modified text

@@
 \usepackage{enumitem}
+\usepackage{lineno}
+\linenumbers
+
 \usepackage{natbib}
+
+\usepackage{fontspec}
+\setmainfont{Georgia}
+%\setsansfont{Trebuchet MS}
+%\setmonofont{Inconsolata}
 
@@
 
+\item Genome scan
 \begin{itemize}
-\item Genome scan
 \item Puget Sound chum salmon populations
@@
 \end{itemize}
+\pagebreak
 
-\pagebreak
 \section*{Abstract}
@@
 Legacy of the salmonid WGD - Uncharacterized regions of the genome - retained through unknown mechanisms.
+
 Recent studies have shown the benefits of polyploidy in other species \citep{Selmecki2015}.
@@
 
-map-assisted genome scan with a paired population design
+\subsection*{Genome scan}
+map-assisted genome scan with a paired population design.
+The linkage map will be used to interpret the population genomic data.
+They provide information on the genomic adjacency of loci and facilitate the  assessment of statistical independence between alleles.
+This can address the persistent problem of pseudoreplication, such as during the estimation of effective population size (e.g., \citet{Larson2014} or for marker development for mixed stock analysis.
+Kernel smoothing and bootstrapping (e.g., \citet{Hohenlohe2010} will be used to identify genomic regions with elevated level of divergence.
 
-\subsection*{Puget Sound chum salmon populations}
-Population structure
+draw on synteny / orthology
 
-Salmonids in the Pacific Northwest have a rich variety of life histories, with variation in run-timing, straying rates, age at maturity, freshwater residence, and many other dimensions \citep{Quinn2005}.
-This species and population-level diversity adds resilience to ecosystems and to species of conservation and economic concern \citep{Schindler2010}, especially in the face of climate change (reviewed in \citet{Schindler2015}).
+\subsubsection*{Puget Sound chum salmon}
 
@@
 The Hood Canal summer-run ESU is composed of 16 historic populations, 7 of which are extinct \citep{Good2005} and is the earliest-returning chum salmon stock in the Americas.
+Further work on Population structure?
 
@@
 Notice which populations where supplemented by hatchery programs?
-Chum salmon stray at similar rates to other pacific salmon \cite{Small2014} (could also cite Johnson et. al. 1997).
+Chum salmon stray at similar rates to other pacific salmon \cite{Small2014} (could also cite Johnson et. al. 1997).  Note past measures of Effective population size.
 
-eggs deposited nov-dec
-embryos devlop and hatch after ~4 months coupled with a migration to sea.
-'survival and growth in juvenile chum salmon depend less on freshwater conditions than on favorable estuarine and marine conditions.'
-return to spawn at 3-5 years of age, spawn within 100km of the ocean
+Salmonids in the Pacific Northwest have a rich variety of life histories, with variation in run-timing, straying rates, age at maturity, freshwater residence, and many other dimensions \citep{Quinn2005}.
+This species and population-level diversity adds resilience to ecosystems and to species of conservation and economic concern \citep{Schindler2010}, especially in the face of climate change (reviewed in \citet{Schindler2015}).
+Life history differs across populations within Puget Sound.
+Generally, eggs are deposited in November - December.
+Embryos devlope and hatch after ~4 months and migrate to sea.
+'survival and growth in juvenile chum salmon depend less on freshwater conditions than on favorable estuarine and marine conditions.'  Chum salmon return to freshwater to spawn at 3-5 years of age, and generally spawn within 100km of the ocean.
 
-Effective population size
-
-\subsection*{Interpretation}
-The linkage map will be used to interpret the population genomic data.
-They provide information on the genomic adjacency of loci and facilitate the  assessment of statistical independence between alleles.
-This can address the persistent problem of pseudoreplication, such as during the estimation of effective population size (e.g., \citet{Larson2014} or for marker development for mixed stock analysis.
-Kernel smoothing and bootstrapping (e.g., \citet{Hohenlohe2010} will be used to identify genomic regions with elevated level of divergence.
-
-draw on synteny / orthology
+\subsection*{Intro wrap-up / Objectives}
 
@@
 \subsection*{Sequence analysis}
-SNPs were identified and genotyped with a reference-based approach with the Stacks software pipeline \cite{Catchen2013}.
-Reference constructed from \citet{Waples2015}.
-Reads from each individual were aligned to the reference with BWA-mem  \citep{Li2013}  Alignments with indels or with a mapping quality < 30 were removed.
-Stacks components pstacks, cstacks, sstacks and populations were used to identify, genotype SNPs, and assign sequence haplotypes for each population collection.
+Genetic variation was quantified with a reference-based approach using the \texttt{Stacks} software pipeline \citep{Catchen2013}.
+A chum salmon reference constructed from \citep{Waples2015}.
+Reads from each individual were aligned to the reference with BWA-mem  (version 0.7.5a-r405) \citep{Li2013}.
+Alignments containing indels or with a mapping quality (MAPQ) < 20 were removed.
+Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each population individual.
+See supplemental file XXX for detailed description of the analysis pipeline.
 
-Filter genotypes and individuals to produce final data set (does allelic bias filtration have a place here?)
+PLINK (version v1.90b3q) \citep{Chang2014} was used to filter genotypes.
+Loci or individuals with more than 25\% missing data were removed.
+Loci with a minor allele frequency below 5\% were removed.
+Hardy-Weinberg equilibrium was tested within each collection using the mid p-value statistic \citep{Graffelman2013}.
+Loci rejecting HWE in more than 5 collections were removed.
+Finally, within each RAD locus, only the single SNP with the largest minor allele frequency was retained, to reduced pseudo-replication caused by physical linkage.
+Note that for for the dominant coding used for the PCA analyses of population structure (see below), sequence haplotypes containing all SNPs within each locus were utilized.
 
@@
 
-Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)
+Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentiation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)
 
-Effective population size was estimated for each population using the LD method implemented in the LDNe software package \cite{Waples2010}.
+Effective population size was estimated for each population using the LD method implemented in the LDNe software package \citep{Waples2010}.
 The LD methods estimates average correlation of alleles at pairs of loci (r2).
@@
 \subsection*{Individual-based analyses} 
-Genotyping duplicate loci using the dominance coding suggested by \cite{Patterson2006}.
+Scoring paralogs using the dominance coding suggested by \citet{Patterson2006} for microsatellites.
 
-PCAs - How do these two methods compare? - maybe measure info loss?
+Principal component analyses (PCAs) were conducted with EIGENSOFT (version 6.0.1) \citep{Patterson2006}
 
-Use a Procrustes analysis to find an optimal transformation.
-This allows the superimposition of one result onto another set of axes, through rotation and stretching this produces a procrustes similarity measure \cite{Peres2001}.
-Other option is a CCA (canonical correlation analysis).
+PCAs were compared with a Procrustes analysis.
+When supplied with two PCA projections, this method attempts to find an optimal superimposition of both of them, this is achieved by  translation, rotation, reflection and scaling.
+After this transformation is complete, the remaining difference in shape is a measure of the Procrustes distance between the projections \citep{Peres2001}.
 
-Formal tests for population structure - Tracey-Widom stats \citep{Tracy1994}.
+Formal tests for population structure \citep{Patterson2006}, based on the Tracey-Widom distribution \citep{Tracy1994}.
 
@@
 
-We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 4x, 3x) with the programs LEPmap \citep{Rastas2013} and MSTmap \citep{Wu2008}.
-This linkage map is novel and builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
-The Kosambi mapping function \citep{Kosambi1943} will be used to relate recombination fraction to genetic distance  due to the presence of strong recombination interference in salmonid chromosome arms \citep{Thorgaard1983}.
+We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 34, 31) with the  LEPmap \citep{Rastas2013}.
+This linkage map  builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
+As the linkage map is constructed from gynogenetic haploid offspring, it only reflects recombination events that occur within the female lineage.
+As with many other species, there are sex-specific differences in recombination rates.
+(Not sure what else to say about female/male differences in linkage maps).
 The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).
@@
 \subsection*{Synteny - relation to genetic resources}
-
-Contigs assembled from paired-end sequence data \citet{Waples2015} will be aligned to genomic resources including the Atlantic salmon genome (Willie Davidson, personal communication), chum transcriptome \citep{Seeb2011}, as well as linkage maps of Chinook salmon (McKinney et al.
-in prep).
 By design, RADseq generates sequence data exclusively near restriction enzyme cut sites; alignments of RAD contigs to genomic resources relate RAD data to much larger genomic sections.
@@
 
-Othologous loci in Chinook salmon
+(pending)
+Contigs assembled from paired-end sequence data \citet{Waples2015} will be aligned to genomic resources including the Atlantic salmon genome (Willie Davidson, personal communication), chum transcriptome \citep{Seeb2011}
 
-annotation drawn from \citep{Waples2015}
+Othologous loci in Chinook salmon linkage maps of Chinook salmon (McKinney et al. submitted).  More detail on the Oxford grid construction and alignment parameters.
 
@@
 \subsection*{Linkage map}
-Here we present a consensus map placing XXX loci onto 37 linkage groups.
+Here we present a consensus map placing 7795 loci onto 37 linkage groups.
 These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in chum salmon \citep{Phillips2001}.

### 2015-10-13 paper/main.tex
update paper

@@
 
-\usepackage{fontspec}
-\setmainfont{Georgia}
+%\usepackage{fontspec}
+%\setmainfont{Georgia}
 %\setsansfont{Trebuchet MS}
@@
 
-\subsection*{Intro wrap-up / Objectives}
+\subsection*{Objectives}
 
@@
 A chum salmon reference constructed from \citep{Waples2015}.
-Reads from each individual were aligned to the reference with BWA-mem  (version 0.7.5a-r405) \citep{Li2013}.
-Alignments containing indels or with a mapping quality (MAPQ) < 20 were removed.
+Reads from each individual were demultiplexed and quality filtered with 'process-radtags' and then aligned to the reference with BWA-mem  (version 0.7.5a-r405) \citep{Li2013}.
+Alignments containing indels or with a mapping quality < 20 were removed.
 Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each population individual.
-See supplemental file XXX for detailed description of the analysis pipeline.
 
-PLINK (version v1.90b3q) \citep{Chang2014} was used to filter genotypes.
+The initial set of genotypes and individuals was assessed prior to further analysis.
 Loci or individuals with more than 25\% missing data were removed.
@@
 Finally, within each RAD locus, only the single SNP with the largest minor allele frequency was retained, to reduced pseudo-replication caused by physical linkage.
+All filters were applied in PLINK (version v1.90b3q) \citep{Chang2014}.
 Note that for for the dominant coding used for the PCA analyses of population structure (see below), sequence haplotypes containing all SNPs within each locus were utilized.
+See supplemental file XXX for detailed description of the analysis pipeline.
 
@@
 
-\subsection*{Population-based analyses}
-
-MAF, Heterozygosity
-
-phylogenetic tree
-
-Genome scan - gloabal or paired populations -
-
-Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentiation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010)
-
-Effective population size was estimated for each population using the LD method implemented in the LDNe software package \citep{Waples2010}.
-The LD methods estimates average correlation of alleles at pairs of loci (r2).
-The mean pairwise r2 value across unlinked loci provides an estimate of contemporary effective population size.
-The linkage map was used to ensure that only pairs of loci not co-located on a chromosome were used to calculate mean r2.
+\subsection*{Linkage map}
+We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 34, 31) with the  LEPmap \citep{Rastas2013}.
+This linkage map  builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
+As the linkage map is constructed from gynogenetic haploid offspring, it only reflects recombination events that occur within the female lineage.
+As with many other species, there are sex-specific differences in recombination rates.
+(Not sure what else to say about female/male differences in linkage maps).
+The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).
 
@@
 
-Formal tests for population structure \citep{Patterson2006}, based on the Tracey-Widom distribution \citep{Tracy1994}.
+Formal tests for population structure \citep{Patterson2006}, based on the Tracey-Widom distribution \citep{Tracy1994}. Q values.
 
-\subsection*{Linkage map}
+\subsection*{Population-based analyses \& genome scans}
+Allele frequencies, Heterozygosity, and Fst (Weir 1984) were calculated for each locus in PLINK.
 
-We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 34, 31) with the  LEPmap \citep{Rastas2013}.
-This linkage map  builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
-As the linkage map is constructed from gynogenetic haploid offspring, it only reflects recombination events that occur within the female lineage.
-As with many other species, there are sex-specific differences in recombination rates.
-(Not sure what else to say about female/male differences in linkage maps).
-The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).
+Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentiation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010).
+
+Genome scans.  Bayescan all populations - 
+LFMM models with run-timing data
+
+Effective population size was estimated for each population using the LD method implemented in the LDNe software package \citep{Waples2010}.
+The LD methods estimates the average correlation of alleles at pairs of loci (r2).
+The mean pairwise r2 value across independently-assorting loci provides an estimate of contemporary effective population size.
+Only loci placed on the linkage map were used for this calculation and the map was utilized to ensure that only pairs of loci not co-located on a chromosome contributed to mean r2.
 
@@
 
+\subsection*{Should I do?}
+phylogenetic tree
+
 \section*{Results}
+\subsection*{Sequencing and genotyping}
+table of sequencing results -  by collection location, including family and wild samples.
+Genotyping rate
 
-Genotyping rate
+\subsection*{Individual-based}
+
 \subsection*{Population-based}
@@
 \begin{figure}[H]
-\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
+\includegraphics[scale=.3]{figures/supplemental/ascertainment2.png}
 \caption{Minor allele frequency (MAF) density histograms for all loci (blue) and the subset of loci placed on the linkage map (green).
@@
 
-Of the xxx loci scored in wild collectionsm, xxx were placed on the linkage map, and covering all LGs.
+Of the 13,407 loci scored in the wild, 6,251 were placed on the linkage map.
 
-A total of xxx paralogs were identified and placed onto the linkage map.
+A total of xxx paralogs were identified and placed onto the linkage map (do I want to count them in pairs or not?).
 The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015} (also McKinney submitted).

### 2015-10-21 paper/main.tex
paper update

@@
 \usepackage{lineno}
-\linenumbers
-
 \usepackage{natbib}
 
+\usepackage{booktabs}
+\usepackage{pdflscape}
 %\usepackage{fontspec}
@@
 
+\linenumbers
 \begin{document}
@@
 
+\listoffigures
+
+\listoftables
+
+\pagebreak
+\section*{Figures}
+\subsection*{Map of sampling locations including run timing}
+\begin{figure}[H]
+\includegraphics[scale=.6]{figures/collection_map.png}
+\caption[Collection locations]{Collection locations and runtiming of chum salmon sampled near Puget Sound.}
+\end{figure}
+
+\subsection*{Linkage map}
+\begin{figure}[H]
+\includegraphics[scale=.26]{figures/chum_map.png}
+\caption[Linkage map of chum salmon]{37 linkage groups, likely corresponding to the 37 chromosomes in the chum salmon karyotype.
+Paralogous loci are shown as red diamonds, non-paralogs are blue circles.
+Black lines connect confounded catalog entries that have been resolved into two paralogous loci.
+The 16 distal concentrations of paralogs form 8 pairs of homeologous chromosomes.
+Notice LGs 2 and 32 have distinct ancestral relationships on each end.}
+\end{figure}
+
+\subsection*{Ascertainment bias}
+\begin{figure}[H]
+\includegraphics[scale=.5]{figures/supplemental/ascertainment.png}
+\caption[MAF Histogram showing ascertainment bias]{Folded minor allele frequency (MAF) for all loci (grey) and the subset of loci placed on the linkage map (black outline).
+The rightward shift in the MAF distribution shows the effect of ascertainment bias.
+Notice the y-axis is density-scaled to accommodate differing number of loci in each set.}
+\end{figure}
+
+\subsection*{Population structure}
+\begin{figure}[H]
+\includegraphics[scale=.35]{figures/poster_3a.png}
+\includegraphics[scale=.35]{figures/poster_3b.png}
+\includegraphics[scale=.35]{figures/poster_3c.png}
+\caption[Individual-based PCAs showing population structure]{Population structure - Individual-based PCA from ten populations (colors) of chum salmon from Puget Sound.
+Population structure obtained from paralogs (a) is similar to that obtained by non-paralogs (b), especially after down-sampling to match the number of loci (c).}
+\end{figure}
+
+\begin{landscape}
+\subsection*{Manhattan plot}
+\begin{figure}[H]
+\includegraphics[scale=.25]{figures/Bayescan_Fst_and_bootstrap.png}
+\caption[Manhattan plot]{Manhattan plot of differentiation across the 37 linkage groups of chum salmon.
+Points are Bayescan Fst values for single loci.
+Population genetic statistics were calculated at each cM position by calculating an inverse distance-weighted average value from loci within a 5cM wide window centered on each position.
+Black outlines show loci selected as life history outliers in Bayescan.
+Black Lower shaded regions show genomic regions in the upper 99\%, as determined by bootstrap permutation.
+Color codes for shaded regions: Red: LFMM qvalue, Blue: Bayescan qvalue, Green: Bayescan Fst, Purple: Weir Fst.}
+\end{figure}
+\end{landscape}
+\section*{Tables}
+
+\subsection*{Sequencing and genotyping}
+
+\begin{table}[H]
+\caption{\label{tab:table-name}Sample sizes. usable sequences, and genotyping rates}
+
+\begin{tabular}{lrrrrr}
+\toprule
+{} & {} & \multicolumn{2}{c}{Aligned sequences} & \multicolumn{2}{c}{Genotyping rate}\\
+Collection &  n   &            mean &        std &              mean &       std \\
+\midrule
+Hamma Hamma            &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
+Lilliwaup Creek        &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
+Nisqually Kalama Creek &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
+Sherwood River Fall    &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
+Sherwood River Summer  &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
+Skookum Creek          &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
+Snohomish River        &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
+Squakum Creek          &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
+Stillaguamish River    &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
+Hoodsport Hatchery*    &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
+\bottomrule
+\multicolumn{6}{l}{*paired-end sequencing.}
+\end{tabular}
+
+\end {table}
+
+\subsection*{Genetic diversity}
+
+\begin{table}[H]
+%\caption{\label{tab:table-name}Genetic diversity}
+\caption{Genetic diversity} 
+\begin{tabular}{lrr}
+\toprule
+{} & Heterozygosity &     Ne \\
+\midrule
+Hamma Hamma            &           0.30 &    339 \\
+Lilliwaup Creek        &           0.34 &  5,959 \\
+Nisqually Kalama Creek &           0.32 &    161 \\
+Sherwood River Fall    &           0.33 &    319 \\
+Sherwood River Summer  &           0.31 &    145 \\
+Skookum Creek          &           0.33 &  1,788 \\
+Snohomish River        &           0.32 &  2,122 \\
+Squakum Creek          &           0.31 & $\infty$* \\
+Stillaguamish River    &           0.30 &  1,001 \\
+Hoodsport Hatchery     &           0.30 & $\infty$* \\
+\bottomrule
+\multicolumn{3}{l}{*small sample size (\textless10)}
+\end{tabular}
+
+\end {table}
+
+\pagebreak
 \section*{Outline}
@@
 \end{itemize}
+
 \pagebreak
@@
 Legacy of the salmonid WGD - Uncharacterized regions of the genome - retained through unknown mechanisms.
-
-Recent studies have shown the benefits of polyploidy in other species \citep{Selmecki2015}.
-Possible benefits are unknown but could include reduced inbreeding depression in small isolated populations typical of salmonids.
 
@@
 The Hood Canal summer-run ESU is composed of 16 historic populations, 7 of which are extinct \citep{Good2005} and is the earliest-returning chum salmon stock in the Americas.
-Further work on Population structure?
 
@@
 Notice which populations where supplemented by hatchery programs?
-Chum salmon stray at similar rates to other pacific salmon \cite{Small2014} (could also cite Johnson et. al. 1997).  Note past measures of Effective population size.
+Chum salmon stray at similar rates to other pacific salmon \cite{Small2014}.
 
@@
 Generally, eggs are deposited in November - December.
-Embryos devlope and hatch after ~4 months and migrate to sea.
-'survival and growth in juvenile chum salmon depend less on freshwater conditions than on favorable estuarine and marine conditions.'  Chum salmon return to freshwater to spawn at 3-5 years of age, and generally spawn within 100km of the ocean.
+Embryos develop and hatch after ~4 months and migrate to sea, with survival and growth very dependent on favorable estuarine and marine conditions  \citep{Quinn2005}.
+Chum salmon return to freshwater to spawn at 3-5 years of age, and generally spawn within 100km of the ocean.
 
-\subsection*{Objectives}
+"genetically similar populations with dissimilar life histories and morphology may provide insights at the onset of ecological speciation and reproductive isolation (Hendry 2009)." - from Aykanat et al.
 
@@
 
+\subsection*{Salish Sea collections}
+The Salish is located in Washington State, USA. The sampling locations and timings were designed to capture the existing diversity in genetic structure and life history.
+
 \subsection*{Sequence analysis}
 Genetic variation was quantified with a reference-based approach using the \texttt{Stacks} software pipeline \citep{Catchen2013}.
-A chum salmon reference constructed from \citep{Waples2015}.
-Reads from each individual were demultiplexed and quality filtered with 'process-radtags' and then aligned to the reference with BWA-mem  (version 0.7.5a-r405) \citep{Li2013}.
+A chum salmon reference was constructed from by conducting an all-by-all self-alignment of the catalog from \citep{Waples2015} using bowtie2 \citep{Langmead2012} allowing up to three mismatches.
+Catalog entries placed on the linkage map of \citet{Waples2015} were retained, otherwise only a single sequence was retained from each group of aligned sequences.
+Reads from each individual were demultiplexed and quality filtered with 'process-radtags' and then aligned to the constructed reference with BWA-mem (version 0.7.5a-r405) \citep{Li2013}.
 Alignments containing indels or with a mapping quality < 20 were removed.
-Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each population individual.
+Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each individual.
 
 The initial set of genotypes and individuals was assessed prior to further analysis.
-Loci or individuals with more than 25\% missing data were removed.
-Loci with a minor allele frequency below 5\% were removed.
-Hardy-Weinberg equilibrium was tested within each collection using the mid p-value statistic \citep{Graffelman2013}.
-Loci rejecting HWE in more than 5 collections were removed.
-Finally, within each RAD locus, only the single SNP with the largest minor allele frequency was retained, to reduced pseudo-replication caused by physical linkage.
-All filters were applied in PLINK (version v1.90b3q) \citep{Chang2014}.
-Note that for for the dominant coding used for the PCA analyses of population structure (see below), sequence haplotypes containing all SNPs within each locus were utilized.
-See supplemental file XXX for detailed description of the analysis pipeline.
-
-Paralogous loci were identified by through their segregation patterns as in \citet{Waples2015}.
-At each locus, the observed allelic segregation pattern were fit to models specified by parental genotypes.
+Loci and individuals with more than 25\% missing data were removed.
+Loci with a minor allele frequency (MAF) below 5\% were removed as they are more difficult to distinguish from sequencing errors \citep{Nielsen2011} .
+Hardy-Weinberg equilibrium (HWE) was tested within each collection using the mid p-value statistic \citep{Graffelman2013}.
+Loci with HWE rejected in more than 5 collections were removed.
+Finally, within each locus, only the single SNP with the largest minor allele frequency was retained, to reduced pseudo-replication caused by physical linkage.
+All filters were applied in \texttt{PLINK} (v1.90beta) \citep{Chang2014}.
+Note that for the PCA analyses of population structure (see below), allelic haplotypes of all SNPs within each locus were utilized.
 
 \subsection*{Linkage map}
-We constructed a consensus linkage map from three gynogenetic haploid families (sizes 175, 34, 31) with the  LEPmap \citep{Rastas2013}.
-This linkage map  builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
-As the linkage map is constructed from gynogenetic haploid offspring, it only reflects recombination events that occur within the female lineage.
-As with many other species, there are sex-specific differences in recombination rates.
-(Not sure what else to say about female/male differences in linkage maps).
-The position of centromeres within each chromosome will be estimated by measuring recombination fractions along chromosomes (cite Limborg?).
+We constructed a consensus linkage map from three families of gynogenetic haploid offspring (family sizes 175, 34, 31) using the software LEPmap \citep{Rastas2013}.
+This linkage map here builds on the map presented in \citet{Waples2015} with the addition of two additional families and the inference of centromeric regions.
+As the linkage map is constructed from gynogenetic haploid offspring, it reflects only the recombination events that occur within the female lineage.
+As with many other species, there are sex-specific differences in recombination rates not reflected in this map.
+Regions of each chromosome likely to contain the centromere are estimated by measuring recombination fractions along chromosomes \textbf{cite Limborg}.
 
-\subsection*{Individual-based analyses} 
-Scoring paralogs using the dominance coding suggested by \citet{Patterson2006} for microsatellites.
+Paralogous loci confounded by alignment were identified and resolved using their segregation pattern within the gynogenetic offspring as in \citet{Waples2015} and were included when constructing the linkage map.
+For all loci that were variable in at least one offspring, the observed allelic segregation pattern was fit to the predicted segregation patterns under different possible parental genotypes.
+The parental genotype was selected as the genotype that was most likely to produced the observed segregation pattern, accounting for genotyping error.
+This parental genotype was used identified segregating loci suitable for inclusion on the linkage map.
 
-Principal component analyses (PCAs) were conducted with EIGENSOFT (version 6.0.1) \citep{Patterson2006}
+\subsection*{Population structure and diversity}
 
+Allele frequencies, Heterozygosity, and Fst \citep{Weir1984} were calculated for each locus in \texttt{PLINK}.
+
+Principal component analyses (PCAs) were conducted on genotype matrices with \texttt{EIGENSOFT} (v6.0.1) \citep{Patterson2006}, including tests for population structure by comparing largest eigenvalues to the Tracey-Widom distribution \citep{Tracy1994}.
+Genotypes at paralogous loci were scored for the presence/absence of each allelic haplotype using the dominance coding suggested by \citet{Patterson2006}.
 PCAs were compared with a Procrustes analysis.
-When supplied with two PCA projections, this method attempts to find an optimal superimposition of both of them, this is achieved by  translation, rotation, reflection and scaling.
-After this transformation is complete, the remaining difference in shape is a measure of the Procrustes distance between the projections \citep{Peres2001}.
+When supplied with two PCA projections, this method attempts to find an optimal superimposition, achieved by translation, rotation, reflection and scaling.
+After this transformation is complete, the remaining difference in shape is a measure of the Procrustes distance between the PCA projections.
+\citep{Peres2001}.
 
-Formal tests for population structure \citep{Patterson2006}, based on the Tracey-Widom distribution \citep{Tracy1994}. Q values.
+Effective population size (Ne) was estimated for each population using the LD method implemented in the \texttt{LDNe} software package \citep{Waples2010}.
+The LD method estimates the average correlation of alleles at pairs of loci (r2).
+The mean pairwise r2 value across independently-assorting loci provides an estimate of contemporary effective population size.
+Physically linked loci can downwardly bias Ne estimates; to avoid this potential bias, only loci placed on the linkage map were included in this analysis, and r2 measurements between loci co-located on a chromosome were also excluded.
 
-\subsection*{Population-based analyses \& genome scans}
-Allele frequencies, Heterozygosity, and Fst (Weir 1984) were calculated for each locus in PLINK.
+\subsection*{Genome scans}
+Rolling-means of populations and test statistics were calculated at each cM position using a sliding-window analysis.
+At each focal cM a weighted-mean value was calculated across all loci within 2.5cM on either side, with weights for each locus within the window inversely proportional to squared distance to the focal point.
+At each focal cM, bootstrapped upper 99\%?
+intervals were calculated by permuting random loci 1000 times into the windowed positions.
 
-Fst across the genome.  Use LOESS (local regression) to reveal regions of elevated differentiation.  Benefits of this approach vs a bootstrapping methods (eg. Hohenlohe 2010).
+LFMM
 
-Genome scans.  Bayescan all populations - 
-LFMM models with run-timing data
-
-Effective population size was estimated for each population using the LD method implemented in the LDNe software package \citep{Waples2010}.
-The LD methods estimates the average correlation of alleles at pairs of loci (r2).
-The mean pairwise r2 value across independently-assorting loci provides an estimate of contemporary effective population size.
-Only loci placed on the linkage map were used for this calculation and the map was utilized to ensure that only pairs of loci not co-located on a chromosome contributed to mean r2.
+Genome scans.  Bayescan all populations - LFMM models with run-timing data
 
@@
 These resources often have functional annotations, whole gene sequences, and reading frame information that is unavailable to RADseq projects, expanding my ability to interpret genetic differentiation in a biological context.
-
-(pending)
-Contigs assembled from paired-end sequence data \citet{Waples2015} will be aligned to genomic resources including the Atlantic salmon genome (Willie Davidson, personal communication), chum transcriptome \citep{Seeb2011}
-
-Othologous loci in Chinook salmon linkage maps of Chinook salmon (McKinney et al. submitted).  More detail on the Oxford grid construction and alignment parameters.
-
-\subsection*{Should I do?}
-phylogenetic tree
 
@@
 
-\subsection*{Individual-based}
-
-\subsection*{Population-based}
-population structure
-
-Summarize population relationships, consistent with \citet{Small2014}?
-
-Breakdown of population structure and lower PC axes.
-
-Four individual-based PCA figures
-
-\includegraphics[scale=.3]{figures/PCA_codom.png}
-\includegraphics[scale=.3]{figures/PCA_dom.png}
-
-\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
-\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
-Paralogs have similar neutral patterns of population structure (Procrustes similarity xxx)
-
-Is the a possible quantitative measure of information loss due to dominance coding?  These doesn't quite make sense, as the the dominant haplotypes contain *more* information.
-
-discuss population vs individual based results
-
-can we demonstrate contained within paralogs by bootstrapping 
-Genome scans - LG regions highlighted.
-
-\subsection*{Effective population size}
-
-Perhaps run the Ne with and without the linkage map correction?
-
-\subsection*{Ascertainment Bias}
-The linkage map was constructed from three female parents from Hoodsport hatchery, WA.
-
-Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
-
-\begin{figure}[H]
-\includegraphics[scale=.3]{figures/supplemental/ascertainment2.png}
-\caption{Minor allele frequency (MAF) density histograms for all loci (blue) and the subset of loci placed on the linkage map (green).
-The rightward shift in the MAF distribution shows the effect of ascertainment bias.} \textbf{TODO: align histogram bins, check the .5 boundary}
-\end{figure}
-
 \subsection*{Linkage map}
 Here we present a consensus map placing 7795 loci onto 37 linkage groups.
-These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in chum salmon \citep{Phillips2001}.
-\textbf{Do we want a map figure, perhaps just a slice of a single LG, or a table?}.
-
+These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in the most common chum salmon karyotype\citep{Phillips2001}.
 Of the 13,407 loci scored in the wild, 6,251 were placed on the linkage map.
 
-A total of xxx paralogs were identified and placed onto the linkage map (do I want to count them in pairs or not?).
-The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015} (also McKinney submitted).
-Consistency across families (see supplemental table xx)
-
-The consensus linkage map produced in chapter two will likely be similar to the single-family map produced in chapter one.
-The map produced in chapter one contained thousands of loci placed on 37 linkage groups, with eight pairs of homeologous chromosome arms.
-These pairs have elevated levels of sequence identity, likely due to ongoing tetrasomic inheritance.
-We expect to find a similar pattern in the other two families, this would provide validation of the methods developed in chapter one.
-Potentially more interesting, but less likely, are drastic differences such as chromosomal inversions or chromosome number polymorphisms.
-This type of chromosomal variation is documented within some salmon species \citep{Phillips2001}, but is not likely to be seen between these closely related families from Hoodsport Washington.
+A total of \textbf{xxx} paralogs were identified and placed onto the linkage map.
+The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015}.
+These eight pairs of homeologous chromosome arms have elevated levels of sequence identity, likely due to ongoing residual tetrasomic inheritance.
 
@@
 
-Notice the distribution of paralogs matches the  pattern found in other salmonids.
 syntenic/orthologous relationships, see supplemental figure xx.
 
-Table (supplemental?)
+\subsection*{Ascertainment Bias}
+The linkage map was constructed from three females from the Hoodsport hatchery, WA.  Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
+
+\subsection*{Genetic diversity}
+
+\subsection*{Population structure}
+
+Population struture represented by the PCA projections was consistent with \citet{Small2014}?.
+Population structure was similar across the paralogs across the duplicated and non duplicated loci.
+Four individual-based PCA figures.
+
+Population structure  have similar neutral patterns of population structure (Procrustes similarity xxx)
 
 \section*{Discussion}
-To do
+
+Recent studies have shown the benefits of polyploidy in other species \citep{Selmecki2015}.
+Possible benefits are unknown but could include reduced inbreeding depression in small isolated populations typical of salmonids.
 
@@
 
-\section*{Meta}
-Does this turn into two papers?
-
- - linkage map and individual-based analyses - including duplicated loci
-
- - inference of adaptation -associated  life history variation  - Fst across the genome.
+discuss population vs individual based results
 
@@
 \section*{Supplemental Figures}
+\begin{itemize}
+\item Figures
+    	\begin{enumerate}
+        \item Linkage map
+        \item Manhattan plots - genome scans statistics
+        \item Cross-validation error of inferred ancestry  - how to select K
+        \item Chinook synteny oxford grid
+        \item PCA of mapped/unmapped loci to address ascertainment bias?
+		\end{enumerate}
+\item Tables
+    	\begin{enumerate}
+        \item Chum reference sequence (FASTA)
+        \item Locus-specific info: 
+        	\begin{itemize}
+            \item Map position
+            \item Allele frequencies
+            \item F-statistics
+            \item Bayescan q value and alphas
+            \item LFMM q value
+            \end{itemize}
+        \item PCA projections, SNP loadings, Procrustes analysis, Tracy-Widom statistics
+        \item LFMM inferred latent factors and environmental variables
+        \item Smoothed genomic statistics from genome scan - 
+        \end{enumerate}
+\end{itemize}
 
@@
 \includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
-\caption{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.  Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
+\caption[SUPPLEMENTAL - PCA eigenvalues]{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.
+Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
 \end{figure}
@@
 \includegraphics[scale=.4]{figures/supplemental/TW_stats.png}
-\caption{Number of significant PC axes as determined by the Tracey-Widom test.}
+\caption[SUPPLEMENTAL - PCA significant axes]{Number of significant PC axes as determined by the Tracey-Widom test.}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[scale=.25]{figures/supplemental/synteny_chinook.png}
-\caption{Oxford grid - Chum and Chinook linkage groups. Loci are colored by their LG assignment in chum salmon and positioned according to the order within each genome.}
+\includegraphics[scale=.35]{figures/supplemental/synteny_chinook.png}
+\caption[SUPPLEMENTAL - Chum / Chinook Oxford grid]{Oxford grid - Chum and Chinook linkage groups.
+Loci are colored by their LG assignment in chum salmon and positioned according to the order within each genome.}
 \end{figure}
-
-% \section*{References}
 
@@
 \section*{Acknowledgements}
+WDFW - chum salmon expertise.
 Carita Pascal - lab work and library prep.
-
-Seeb lab
-
-WDFW - chum salmon expertise.
-
+Samples sources?
 Rachel Hovel - multivariate stat advice.

### 2015-10-27 paper/main.tex
rerun LFMM

@@
 
-draw on synteny / orthology
+Despite the limited geogrpahic range of this studym
+
+LFMM and other methods of environmental correlation have increased power to detect selection from standing genetic variation (Pritchard2010, Frichot2013)
 
@@
 \subsection*{Salish Sea collections}
-The Salish is located in Washington State, USA. The sampling locations and timings were designed to capture the existing diversity in genetic structure and life history.
+Colections of chum salmon were made across the Salish Sea, of the Pacific Ocean on the border of the USA and Canada from.
+Collection locations and timings were designed to capture the existing diversity in genetic structure and life history, including the latest-spawning chum salmon population (Nisqually) and the ESA-listed Hood Canal summer spawning population (Hamma Hamma).
+Fin clips were taken from adult fish were collected from each location during a single sampling event and preserved in ethanol.
+
+DNA was extracted from tissues using DNEasy-96 kits from Qiagen (Venlo, Netherlands).
+A total of 200 adult samples were prepared for RAD sequencing with the SbfI restriction enzyme as per Baird et al.
+(2008) and Etter et al.
+(2011a).
+DNA from each sample was uniquely barcoded (6bp), pooled into libraries of 10-30 samples, and sequenced for 101 base cycles at the Genomics Core Facility at the University of Oregon, on a Illumina HiSeq2000.
+Hoodsport samples were sequenced using a paired-end protocol, all other collections were sequenced using a single-end protocol.
+Data from 240 gynogentic haploid offspring, used in construction of the consensus linkage map and originally reported in \citet{Waples2015}, were sequenced in a similar manner.
 
@@
 Stacks components \texttt{pstacks}, \texttt{cstacks}, \texttt{sstacks}, and \texttt{populations} were used to identify and genotype genetic variants for each individual.
+20 individuals, 2 from each collection location, were used to ascertain genetic variation, other samples were genotyped at these loci.
 
@@
 We constructed a consensus linkage map from three families of gynogenetic haploid offspring (family sizes 175, 34, 31) using the software LEPmap \citep{Rastas2013}.
-This linkage map here builds on the map presented in \citet{Waples2015} with the addition of two additional families and the inference of centromeric regions.
+This linkage map here builds on the map presented in \citet{Waples2015} with the addition of two additional families and the placement of centromeric regions.
 As the linkage map is constructed from gynogenetic haploid offspring, it reflects only the recombination events that occur within the female lineage.
@@
 \subsection*{Ascertainment Bias}
-The linkage map was constructed from three females from the Hoodsport hatchery, WA.  Demonstrate ascertainment effect when using only loci on linkage map - effect on allele frequencies.
+The linkage map was   Initial population variant discovery proceeded on two individuals from each population.
+When these disocered snps are filtered by inclusion on the linkage map constructed from three females from the Hoodsport collection there is a notable right-shift in the allele frequency spectrum (Figure 3).
+This occurs as rare variants from other populations are excluded as they were not variable in any of the three parents used for linkage mapping.
 
 \subsection*{Genetic diversity}
+Hamma hamma, the Endangered species act (ESA)-listed collection, and member of a distinct population segment, did not show reduced diversity as measured by hetereozygosity or contemporary Ne.
+
+Two populations has infinite point estimatates of Ne, these two populations were also the two populaitons with the smallest sample sizes, both below ten.  Small sample sizes  with
 
@@
 
-Population struture represented by the PCA projections was consistent with \citet{Small2014}?.
-Population structure was similar across the paralogs across the duplicated and non duplicated loci.
-Four individual-based PCA figures.
+Population structure represented by the PCA projections was consistent with \citet{Small2014}?.
+Population structure, as reflected by the PCA projections, was similar whether measured with the paralogs or non duplicated loci: Procrustes similarity xxx.
 
-Population structure  have similar neutral patterns of population structure (Procrustes similarity xxx)
+The distinctness of the Hamma Hamma summer run chum salmon was well supported in our analyses of population structure.
+In all PCAs, Hamma Hamma individuals were separated from the rest of the indidivuals along one of the primary axes (Figure 4).
+
+Population structure ave similar neutral patterns of population structure
+
+"PCA uses the mean allele frequencies as the first factor, and then two factors that represent deviations from this mean in two orthogonal directions (e.g., the diagonals of the square).
+As a result the PCA loadings on the second and third factors effectively recapitulate the geography of the space, as previously observed.
+...
+In summary, the fact that the first factor in PCA represents the mean allele frequencies is responsible both for the fact that it produces less interpretable factors in the discrete case and more interpretable results in the continuous case.
+" {Engelhardt}
 
 \section*{Discussion}
+
+The potential for bias in genetic inference resulting from this ascertainment bias.
 

### 2015-10-27 scripts/procrustes.R

@@ -8,23 +8,40 @@ library(vegan)
 #rel_mat_1 = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/paralogs.dom.relmatrix', sep = "", header = FALSE)
 #rel_mat_2 = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/on_map.codom.subsample.relmatrix', sep = "", header = FALSE)
 
-evec_1 = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/complete.codom.evec', 
+evec_a = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/paralogs.dom.evec',                        sep = "", header = FALSE, skip =1)
+
+evec_b = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/complete.dom.evec', 
                        sep = "", header = FALSE, skip =1)
-evec_2 = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/complete.dom.evec', 
+evec_c = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/complete.dom.subsample.evec', 
                     sep = "", header = FALSE, skip =1)
 
-evec_3 = read.table('/home/ipseg/Desktop/waples/chum_populations/results/batch_4/EIGENSOFT/paralogs.dom.evec', 
-										sep = "", header = FALSE, skip =1)
 
 # CCA
 my_cca = cc(evec_1[2:5], evec_2[2:6])
 
 
 # procrustes
-proc1 = procrustes( evec_2[2:7], evec_1[2:7], symmetric=TRUE)
-plot(proc1, kind = 2)
-plot(proc1, kind = 1, choices=c(1,2))
-proc1$scale
+proc_ab = procrustes( evec_a[2:7], evec_b[2:7], symmetric=TRUE, )
+summary(proc_ab)
+plot(proc_ab, kind = 2)
+plot(proc_ab, kind = 1, choices=c(1,2))
+
+prot_ab = protest(evec_a[2:7], evec_b[2:7], permutations = how(nperm = 10000))
+prot_ac = protest(evec_a[2:7], evec_c[2:7], permutations = how(nperm = 10000))
[…]

### 2015-10-29 scripts/LEA_analysis.R
reorganize, rerun LFMM, genome scan plots

@@ -5,11 +5,11 @@ ped_genotypes = '/home/ipseg/Desktop/waples/chum_populations/data/batch_4/pop_ge
 lfmm_genotypes = '/home/ipseg/Desktop/waples/chum_populations/results/batch_4/LFMM/non_paralogs.ped.lfmm'
 geno_genotypes = '/home/ipseg/Desktop/waples/chum_populations/results/batch_4/LFMM/non_paralogs.ped.geno'
 
+
 # convert a .ped  file
 ped2lfmm(input.file = ped_genotypes,  output.file = lfmm_genotypes)
 # convert lfmm file to geno
 lfmm2geno(input.file = lfmm_genotypes, geno_genotypes, force = TRUE)
-
 
 # run pca
 pc = pca(lfmm_genotypes, scale = TRUE, center = TRUE)
@@ -33,12 +33,13 @@ snmf_project = snmf(geno_genotypes, K=1:10, entropy = TRUE, repetitions = 3, CPU
 # plot cross-entropy criterion of all runs of the project
 plot(snmf_project, lwd = 5, col = "red", pch=1)
 
+
 # get the cross-entropy of each run for K = 3
 ce = cross.entropy(snmf_project, K = 3)
 # select the run with the lowest cross-entropy
 best = which.min(ce)
 # We can also visualize a barplot of ancestry coeffcients as follows.
-barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8)
+barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8, xlab = 'Individual')
 
 library(plyr)
 pp = data.frame(Q(snmf_project, K = 3, run  =best ))

### 2015-10-29 scripts/LEA_analysis.dom.R

@@ -1,0 +1,87 @@
+# LFMM including duplicated loci (dominance coded)
+
+library("LEA")
+setwd("~/Desktop/waples/chum_populations/results/batch_4/LFMM")
+
+raw_genotypes = '/home/ipseg/Desktop/waples/chum_populations/results/batch_4/LFMM/complete.dom.geno'
+
+lfmm_genotypes = '/home/ipseg/Desktop/waples/chum_populations/results/batch_4/LFMM/complete.dom.lfmm'
+geno_genotypes = '/home/ipseg/Desktop/waples/chum_populations/results/batch_4/LFMM/complete.dom.geno'
+
+
+# convert raw file to lfmm
+geno2lfmm(input.file = raw_genotypes, lfmm_genotypes, force = TRUE)
+
+# convert lfmm file to genonmf
+
+lfmm2geno(input.file = lfmm_genotypes, geno_genotypes, force = TRUE)
+
+# run pca
+pc = pca(lfmm_genotypes, scale = FALSE, center = TRUE)
+par(mfrow=c(1,1))
+
+# Plot eigenvalues.
+plot(pc, lwd=5, col="red",xlab=("PCs"),ylab="eigen")
+# Plot standard deviations.
+plot(pc$sdev)
+# pca projection
+plot(pc$projections[,1], pc$projections[,2])
+
+# Perfom Tracy-Widom tests on all eigenvalues.
+tw = tracy.widom(pc)
+# display the p-values for the Tracy-Widom tests and plot the percentage of variance explained by each component
+plot( -log10(tw$pvalues),tw$percentage)
+
+
+# run snmf (sparse non-negative matrix factorization)
+snmf_project = NULL
+snmf_project = snmf(geno_genotypes, K=2:6, entropy = TRUE, repetitions = 5, CPU = 6, percentage = 0.10, project = "new", ploidy = 1)
+
+# we may want to deal with the 
+
+# plot cross-entropy criterion of all runs of the project
+plot(snmf_project, lwd = 5, col = "red", pch=1)
+
+# get the cross-entropy of each run for K = 3
+ce = cross.entropy(snmf_project, K = 3)
+# select the run with the lowest cross-entropy
+best = which.min(ce)
+# We can also visualize a barplot of ancestry coeffcients as follows.
+barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8, xlab = 'Individual')
+
+
+
+##LFMM##
[…]

### 2015-10-29 scripts/procrustes.R

@@ -33,7 +33,7 @@ prot_bc = protest(evec_b[2:7], evec_c[2:7], permutations = how(nperm = 10000))
 prot_ab
 prot_ac
 prot_bc
-
+prot_bc$t0
 
 summary(prot_bc)
 protest(evec_a[2:7], evec_b[2:7], permutations = how(nperm = 10000))

### 2015-11-14 paper/main.tex
working

@@
 Stillaguamish River    &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
+\midrule
 Hoodsport Hatchery*    &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
@@
 \multicolumn{6}{l}{*paired-end sequencing.}
-\end{tabular}
+5\end{tabular}
 
@@
 Stillaguamish River    &           0.30 &  1,001 \\
+\midrule
 Hoodsport Hatchery     &           0.30 & $\infty$* \\
@@
 \begin{figure}[H]
+%\includegraphics[scale=.35]{figures/supplemental/recombination_landscape.fam_08.png}
+\caption[SUPPLEMENTAL - Centromere placemet - y plots]{ Centromere placemet - y plots}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[scale=.35]{figures/supplemental/synteny_chinook.png}
+\caption[SUPPLEMENTAL - Chum / Chinook Oxford grid]{Oxford grid - Chum and Chinook linkage groups.
+Loci are colored by their LG assignment in chum salmon and positioned according to the order within each genome.}
+\end{figure}
+
+\begin{figure}[H]
 \includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
@@
 \begin{figure}[H]
-\includegraphics[scale=.35]{figures/supplemental/synteny_chinook.png}
-\caption[SUPPLEMENTAL - Chum / Chinook Oxford grid]{Oxford grid - Chum and Chinook linkage groups.
-Loci are colored by their LG assignment in chum salmon and positioned according to the order within each genome.}
+\caption[SUPPLEMENTAL - Genome scan - Bayescan Fst]{ Centromere placemet - y plots}
 \end{figure}
+
+\begin{figure}[H]
+\caption[SUPPLEMENTAL - Q plot - ancestry coefficients]{Ancestry coefficients}
+\end{figure}
+
+\begin{table}[H]
+\caption[SUPPLEMENTAL - centromere placement]{Centromere placement}
+\end {table}
+
+\begin{table}[H]
+\caption[SUPPLEMENTAL - Procrustes analysis]{Procrustes analysis}
+\end {table}
 

### 2015-11-28 paper/main.tex
roate PCA axes to match
update tables 1 and 2

@@
 \begin{figure}[H]
-\includegraphics[scale=.6]{figures/collection_map.png}
+\includegraphics[scale=.6]{figures/collection_map_colors.png}
 \caption[Collection locations]{Collection locations and runtiming of chum salmon sampled near Puget Sound.}
@@
 \begin{figure}[H]
-\includegraphics[scale=.35]{figures/poster_3a.png}
-\includegraphics[scale=.35]{figures/poster_3b.png}
-\includegraphics[scale=.35]{figures/poster_3c.png}
+\includegraphics[scale=.35]{figures/PCA_a.png}
+\includegraphics[scale=.35]{figures/PCA_b.png}
+\includegraphics[scale=.35]{figures/PCA_c.png}
+\includegraphics[scale=.45]{figures/PCA_legend.png}
 \caption[Individual-based PCAs showing population structure]{Population structure - Individual-based PCA from ten populations (colors) of chum salmon from Puget Sound.
@@
 
-\subsection*{Sequencing and genotyping}
-
+% Table 1
 \begin{table}[H]
-\caption{\label{tab:table-name}Sample sizes. usable sequences, and genotyping rates}
-
-\begin{tabular}{lrrrrr}
+\caption{\label{tab:table-name}Sample size. usable sequences, and genotyping rate for each collection}
+\begin{tabular}{llrrrrrr}
 \toprule
-{} & {} & \multicolumn{2}{c}{Aligned sequences} & \multicolumn{2}{c}{Genotyping rate}\\
-Collection &  n   &            mean &        std &              mean &       std \\
+{} & {} & {} & {} & \multicolumn{2}{c}{Usabled sequences} & \multicolumn{2}{c}{Genotyping rate}\\
+Collection &  Run Timing   &  Year &  n &          mean &        std &              mean &       std \\
 \midrule
-Hamma Hamma            &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
-Lilliwaup Creek        &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
-Nisqually Kalama Creek &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
-Sherwood River Fall    &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
-Sherwood River Summer  &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
-Skookum Creek          &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
-Snohomish River        &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
-Squakum Creek          &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
-Stillaguamish River    &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
+Hamma Hamma            &  Summer &  2010 &  20 &         1,419,541 & 1,427,760 &            0.87 &       0.08 \\
+Lilliwaup Creek        &    Fall &  2011 &  20 &         2,760,125 &   999,141 &            0.98 &       0.01 \\
+Nisqually Creek &  Winter &  2003 &  17 &         2,270,022 & 1,432,866 &            0.96 &       0.03 \\
+Sherwood River     &    Fall &  1994 &  32 &         3,235,188 &   966,091 &            0.96 &       0.04 \\
+Sherwood River   &  Summer &  1994 &  31 &         2,504,974 & 1,183,089 &            0.91 &       0.07 \\
+Skookum Creek          &    Fall &  2010 &  11 &         1,644,932 &   637,844 &            0.95 &       0.09 \\
+Snohomish River        &    Fall &  2010 &  14 &         1,135,085 &   495,888 &            0.94 &       0.07 \\
+Squakum Creek          &     Fall &  2010 &   8 &           999,084 &   650,927 &            0.86 &       0.08 \\
+Stillaguamish River    &    Fall &  2010 &  13 &           710,538 &   269,873 &            0.91 &       0.06 \\
 \midrule
-Hoodsport Hatchery*    &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
+Hoodsport Hatchery     &    Fall &  2010 &   8 &           509,422 &   148,391 &            0.85 &       0.08 \\
 \bottomrule
 \multicolumn{6}{l}{*paired-end sequencing.}
-5\end{tabular}
-
+\end{tabular}
 \end {table}
 
-\subsection*{Genetic diversity}
-
+% Table 2
 \begin{table}[H]
-%\caption{\label{tab:table-name}Genetic diversity}
 \caption{Genetic diversity} 
-\begin{tabular}{lrr}
+\begin{tabular}{lrrll}
 \toprule
-{} & Heterozygosity &     Ne \\
+Collection & Obs. Het. &  $\widehat{N_{e}}$ &   lower CI &    upper CI \\
 \midrule
-Hamma Hamma            &           0.30 &    339 \\
-Lilliwaup Creek        &           0.34 &  5,959 \\
-Nisqually Kalama Creek &           0.32 &    161 \\
-Sherwood River Fall    &           0.33 &    319 \\
-Sherwood River Summer  &           0.31 &    145 \\
-Skookum Creek          &           0.33 &  1,788 \\
-Snohomish River        &           0.32 &  2,122 \\
-Squakum Creek          &           0.31 & $\infty$* \\
-Stillaguamish River    &           0.30 &  1,001 \\
+Hamma Hamma            &           0.30 &    339 &   316.5 &    365.8 \\
+Lilliwaup Creek        &           0.34 &  5,959 &  3276.5 &  32651.6 \\
+Nisqually Kalama Creek &           0.32 &    161 &   156.7 &    166.8 \\
+Sherwood River (Fall)    &           0.33 &    319 &   310.8 &    329.5 \\
+Sherwood River (Summer)  &           0.31 &    145 &   142.9 &    147.6 \\
+Skookum Creek          &           0.33 &  1,788 &  1121.0 &   4402.6 \\
+Snohomish River        &           0.32 &  2,122 &  1400.1 &   4379.3 \\
+Squakum Creek          &           0.31 & $\infty$* &     NA &      NA \\
+Stillaguamish River    &           0.30 &  1,001 &   766.0 &   1443.7 \\
 \midrule
-Hoodsport Hatchery     &           0.30 & $\infty$* \\
+Hoodsport Hatchery     &           0.30 & $\infty$* &     NA &      NA \\
 \bottomrule
@@
 \end{tabular}
-
 \end {table}

### 2015-11-30 scripts/LEA_analysis.R
updated figures and results

@@ -41,6 +41,13 @@ best = which.min(ce)
 # We can also visualize a barplot of ancestry coeffcients as follows.
 barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8, xlab = 'Individual')
 
+
+pdf('/home/ipseg/Desktop/waples/chum_populations/paper/figures/supplemental/Q.non_paralogs.pdf')
+barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8, xlab = 'Individual')
+dev.off()
+
+
+
 library(plyr)
 pp = data.frame(Q(snmf_project, K = 3, run  =best ))
 pp = arrange(pp, V4)
@@ -50,7 +57,7 @@ pp = arrange(pp, V1)
 barplot(t(pp), col = 1:8)
 
 
-barplot(t(order(Q(snmf_project, K = 4, run  =best ))), col = 1:4))
+barplot(t(order(Q(snmf_project, K = 3, run  = best ))), col = 1:4)
 
 
 ##LFMM##

### 2015-11-30 scripts/LEA_analysis.dom.R

@@ -47,6 +47,10 @@ best = which.min(ce)
 # We can also visualize a barplot of ancestry coeffcients as follows.
 barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8, xlab = 'Individual')
 
+pdf('/home/ipseg/Desktop/waples/chum_populations/paper/figures/supplemental/Q.complete.pdf')
+barplot(t(Q(snmf_project, K = 3, run  =best )), col = 1:8, xlab = 'Individual')
+dev.off()
+
 
 
 ##LFMM##

### 2016-01-15 scripts/plot_phylo_tree.R
phylo tree

@@ -1,0 +1,52 @@
+source("https://bioconductor.org/biocLite.R")
+source("http://bioconductor.org/biocLite.R")
+biocLite("BiocUpgrade")
+
+biocLite("ggtree")
+
+library("ggtree")
+
+nwk_file = "/home/ipseg/Desktop/waples/chum_populations/results/batch_4/pop_analysis/poptree2/FST_named.nwk"
+tree <- read.tree(nwk_file)
+
+tr <- ggtree(tree, layout="unrooted") + geom_text2(aes(subset=!isTip, label=node), hjust=-.3) + geom_tiplab()
+tr
+tr %>% rotate(11)
+
+tr <- ggtree(tree) + geom_text2(aes(subset=!isTip, label=node), hjust=-.3) + geom_tiplab()
+tr
+flip(tr, 17, 12 ) 
+
+
+tr <- ggtree(tree, layout="unrooted") + ggtitle("unrooted layout") + geom_label(aes(label=node)) 
+tr
+flip(tr, 17, 11 ) 
+
+
+
+
+
+
+
+# Find the internal node number of the input taxas MRCA
+MRCA(tree, tip = c('Hoodsport_Hatchery', 'Lilliwaup_Creek'))
+
+
+ggtree(tree, layout="unrooted") + ggtitle("unrooted layout")    +
+#geom_tiplab(size=6, color="black")      +
+  geom_label(aes(label=node))   %>% flip(12)  +
+#  geom_text(aes(label=label))  
+#  geom_label(aes(label=label))     +
+  add_legend()  + 
+  theme_tree()
+
+ggtree(tree, branch.length="none")
+
+
+
+%>% rotate(21)
+
+
+
+geom_tiplab(aes(angle=angle), size=3, color="black")
++ geom_treescale(fontsize=8, linesize=2, offset=0)
